Titeln på avhandlingens språk

### 2023-03-16 body/part1/chapter2-relatedwork/relatedwork.tex
background
relwork

\subsection{Wearable Cognitive Assistance}

\subsection{Benchmarking and emulation of \glsfmtshort{XR} systems}

\textcite{munro2016aaremu}: Software framework for the emulation of AR on Android devices.
A trace of pre-recorded inputs (video, gyro, GPS) are replayed to the real processing code by mocking Android SDK APIS.
Recordings can be ``interactive'', in which case the trace corresponds to images indexed by directional bearings, i.e.\ a 3D sphere), or non-interactive, in which case the trace corresponds to a video replayed at a customizable framerate.

\textcite{williams2013transform}: Toolkit for visualization of AR and evaluation of tracking algorithms.
Recorded trace is replayed in a virtualized environment.

\textcite{berning2013parnorama}: Inverted emulation.
AR application is emulated, user is real.
AR application emulation corresponds to 360 degree FOV video.
Used for prototyping user interactions in AR.

\textcite{choi2022emulating}: XREmul, input emulation tool for XR.
Similar to \cite{munro2016aaremu}, traces of inputs are pre-recorded and then replayed.
Allows for abstraction of inputs in general classes for device-agnostic inputs.
Paper highlights the challenges of deterministic trace (leaves solution to future work).

\textcite{chetoui2022arbench}: ARBench, a benchmarking suite for AR.
Corresponds to a software package including a multitude of AR workloads, emulating the load placed on the the hardware.
Only considers locally-running AR, not network.
Does not emulate human behavior, uses traces of AR applications.

\textcite{george2020openrtist}: OpenRTiST, benchmarking workload for Edge Computing, AR
Based on stable diffusion.

@@

\todo[inline]{Needs harmonizing.}

>>>>

\subsection{Emulation in \glsfmtshort{XR} research}

Only a limited number of works addressing the partial or complete emulation of XR applications for benchmarking and research purposes exist in literature.
One such work is~\cite{williams2013transform}.
In this, the authors introduced a trace-based toolkit for the evaluation of tracking algorithms in \gls{AR} research and development.
The trace consists of geographical coordinates and accelerometer data as well as video frames which can be replayed on a desktop visualization tool or a smartphone application for the evaluation of tracking algorithms in \gls{AR} research and development.

\cite{munro2016aaremu} presents a trace-based framework that allows a previously recorded trace of inputs to be replayed to the processing components of a real \gls{AR} application by mocking Android \gls{SDK} \glspl{API}.
This approach allows for benchmarking and evaluation of algorithms and architectures on real data.
A similar approach was taken by~\cite{choi2022emulating}, but the authors instead provided developers of \gls{AR} with a framework that abstracts input into general classes, allowing for device-agnostic processing.

Finally,\ \cite{chetoui2022arbench} employed \gls{AR} emulation to evaluate hardware rather than the software implementation itself.
Their tool, \emph{ARBench}, features emulated \gls{AR} workloads that mimic the load placed on the system by real applications.
This approach is similar to the one presented in this dissertation, but it exclusively considers on-device \gls{AR} processing.
Furthermore, the benchmarks are deterministic, and no emulation of realistic human behavior is attempted.

\subsection{Edge and Cloud Benchmarking}

\emph{OpenRTiST}~\cite{george2020openrtist} is a tool for the benchmarking and performance evaluation of Edge Computing deployments using real-time processing of a live video feed.
Video is streamed from a source Android device to a compute node where neural style-transfer~\cite{gatys2016image} is applied to it.
The transformed video is then fed back to the source to be presented, resulting in a compute-intensive, bandwidth-hungry, and latency-sensitive benchmark.

@@
